---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# linearalgebra

<!-- badges: start -->
<!-- badges: end -->

'linearalgebra' aids with basic mathematics used in linear algebra. This package also provides a dataframe with basic linear algebra functions. 

## Installation

You can install the development version of linearalgebra from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("yliu0823/linearalgebra")
```

## Usage

To begin testing the various function, it is required to have a matrix. We'll use the random_matrix_generator to create a random matrix:

```{r,example} 
library(linearalgebra)

A <- random_matrix_generator(3,3,1,5)
A
```


Above we have matrix A, to check if there is a row of 0's, we can use the function below:

```{r}
rows_of_zero_detector(A)
```

We can also check if the matrix is linearly dependent or independent. 

```{r}
linear_dependent_detector(A)
```

If we were wondering how many pivots there is, we can use the function below: 

```{r}
pivot_check(A)
```

If we have a list of vectors and are wondering if they are a basis we can use the function below:

```{r}
# List of vectors
vectors <- list(a = c(1, 2, 3), b = c(4, 5, 6), c = c(7, 8, 9)
)

findBasisFromList(vectors)
```

If you do not know what 'basis' is, you can use the function below:

```{r}
def("basis")
```

