---
title: "Using the linear algebra package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the linear algebra package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
##Checking linear algebra glossary
The main function of the linear algebra package is to let you browse definitions of basic terms in linear algebra. Let's see how we can accomplish this. First, load the `linearalgebra` package.
```{r setup}
library(linearalgebra)
```
You can check the terms with definitions available by subsetting the dataframe glossory.
```{r}
glossary["Terms"]
```
Then, use the `def()` function to retrieve definition of term from the glossary attached to the package.
```{r}
def("Codomain")
```
##Glossary data
The linearalgebra package comes with a built-in data set matching definitions with corresponding terms. 
```{r}
linearalgebra::glossary
```
##Basic operations in Linear Algebra
The linearalgebra package also includes a few functions for basic matrix operations in Linear Algebra. First, `random_matrix_generator()` is useful for generating random matrices. Let's see how we can do this.
```{r}
A <- random_matrix_generator(ncols = 3, nrows = 3, min = 0, max = 10)
```
Through running the `random_matrix_generator()` function, we created a matrix named A. Then, use `rows_of_zero_detector()` to check if the matrix has rows of zero in its rref form.
```{r}
rows_of_zero_detector(A)
```
After this, use `linear_dependent_detector()` to check if the matrix A contains linearly dependent vectors.
```{r}
linear_dependent_detector(A)
```
Also, use `pivot_check()` to count number of pivots of matrix A in its rref form.
```{r}
pivot_check(A)
```
Apart from these matrix operations, use `findBasisFromList()` to find basis of a set of vectors.
```{r}
vectors <- list(
a = c(1, 2, 3),
b = c(4, 5, 6),
c = c(7, 8, 9)
)
findBasisFromList(vectors)
```

